Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-08-16 Ch1_movement_rates/Ch1_markdown.Rmd
Seed locations added

We can look at how those exponential distributions look for each of the individuals in those populations

@@

# range <- c(-0.9,5)
#create density plots
curve(dexp(x, m_1[5]), 
      #from=range[1], to=range[2], 
      col=mycols[1],
      main = 'Exponentially distributed movement lengths for 5 individuals', #add title
      ylab = 'Density', #change y-axis label
      )
for(i in 1:4){
  curve(dexp(x, m_1[i]), 
        #from=range[1], to=range[2],
        col=mycols[i], add=TRUE)
}

@@

tru.rate <- m_1[individual] # In case I want to do scale 1/rate
movedist <- rexp(t, rate = tru.rate)
angle <- runif(t, min = 0, max = 360)
distx <- movedist*cos(angle)
xloc <- c(0, cumsum(distx))
disty <- movedist*sin(angle)
yloc <- c(0, cumsum(disty))
animalTraj <- data.frame(time = 0:t, xloc = xloc, yloc = yloc)

@@

```
```{r}
sim_movement <- function(prm, t = 1000, plot.it = TRUE, return.data.frame = FALSE){
  tru.rate <- round(prm, 3)
  movedist <- rexp(t, rate = tru.rate)
  angle <- runif(t, min = 0, max = 360)
  distx <- movedist*cos(angle)
  xloc <- c(0, cumsum(distx))
  disty <- movedist*sin(angle)
  yloc <- c(0, cumsum(disty))
  animalTraj <- data.frame(time = 0:t, xloc = xloc, yloc = yloc)
  if(plot.it == TRUE){
    plot(x = xloc, y = yloc, type = "l", main = paste("Rate=",tru.rate))
  }
  if(return.data.frame == TRUE){
    return(animalTraj)
  }
}
```

@@

>>>>

We can look at how those exponential distributions look for each of the individuals in those populations.

@@

range <- c(-0.1,15)
#create density plots
curve(dexp(x, 1/m_1[1]), #notice rate for exponential is 1/movement rate.
      from=range[1], to=range[2], 
      col=mycols[1],
      main = 'Exponentially distributed movement lengths for 5 individuals', #add title
      ylab = 'Density', #change y-axis label
      )
for(i in 2:5){
  curve(dexp(x, 1/m_1[i]), 
        from=range[1], to=range[2],
        col=mycols[i], add=TRUE)
}

@@

tru.rate <- m_1[individual] # In case I want to do scale 1/rate
movedist <- rexp(t, rate = 1/tru.rate)
angle <- runif(t, min = 0, max = 360)
distx <- movedist*cos(angle)
xloc <- c(0, cumsum(distx))
disty <- movedist*sin(angle)
yloc <- c(0, cumsum(disty))
animalTraj <- data.frame(time = 0:t, xloc = xloc, yloc = yloc)

@@

```
```{r}
sim_movement <- function(prm, t = 1000, plot.it = TRUE, return.data.frame = FALSE){
  tru.rate <- round(prm, 3)
  movedist <- rexp(t, rate = 1/tru.rate)
  angle <- runif(t, min = 0, max = 360)
  distx <- movedist*cos(angle)
  xloc <- c(0, cumsum(distx))
  disty <- movedist*sin(angle)
  yloc <- c(0, cumsum(disty))
  animalTraj <- data.frame(time = 0:t, xloc = xloc, yloc = yloc)
  if(plot.it == TRUE){
    plot(x = xloc, y = yloc, type = "l", main = paste("Rate=",tru.rate))
  }
  if(return.data.frame == TRUE){
    return(animalTraj)
  }
}
```

@@

Now, we get the animals to disperse seeds. Seeds gut retention time are sampled from a gamma distribution.
```{r eval=FALSE}
nseeds <- 20
grt <- round(rgamma(nseeds, shape = 4, scale = 5))
t.grt <- max(grt)

animalTraj <- sim_movement(m_1[1], t = t.grt, plot.it = FALSE, return.data.frame = TRUE)

# Determine where the seeds are dropped based on the animal's location.
seed_loc <- data.frame(seed_id = 1:nseeds, time = grt)
seed_loc <- merge(animalTraj, seed_loc, by = "time")
seed_loc$dispersal <- sqrt(seed_loc$xloc^2 + seed_loc$yloc^2)

animalTraj %>% 
  ggplot(., aes(x = xloc, y=yloc)) +
  geom_path() +
  geom_point(data=seed_loc, aes(x = xloc, y = yloc))
